Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-30 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

\begin{example}Consider $A=\left(\begin{array}{cc}
1 & 0\\
1 & 1
\end{array}\right)$. Then, 
\begin{equation}
\left\Vert A\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{A}{\psi}\right|=\frac{3}{2}\,.
\end{equation}
\end{example}

>>>>

\begin{example}Consider $A=\left(\begin{array}{cc}
1 & 0\\
1 & 1
\end{array}\right)$. Then, it is easy to verify that $\left\Vert A\right\Vert =3/2$.
On the other hand, its Frobenius norm or Hilbert-Schmidt norm\nb$\left\Vert A\right\Vert _{\mathrm{F}}$
is $\sqrt{3}$\nb\cite{Jaeger2007}; its operator $p$-norms\nb$\left\Vert A\right\Vert _{p}$
are $\left\Vert A\right\Vert _{1}=\left\Vert A\right\Vert _{\infty}=2$
and $\left\Vert A\right\Vert _{2}=\left[\left(3+\sqrt{5}\right)/2\right]^{\frac{1}{2}}$\nb\cite{RobertsVarberg1973,peres1995quantum}.\end{example}
